Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-22 paper-v1.tex
Background: related work.

\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials where performance, though, is assessed only in terms of quantity of reviews but not quality.
\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} that provide scientific peer review and also peer-reviews of the reviews. 
Spearpoint\cite{ResearchCoin} proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees. \emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process. Avital \cite{AvitalToken} suggests a token-based peer-review payment system. \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process. The system implements cryptoeconomical incentives for building reputation in the community of users. \newline Other proposals to improve the peer-review system have instead focused on features such as decentralization \cite{DecentralSc2,DecentralSc1}, security \cite{Pevo,CryptSubmit,MarsChain}.

@@

Here we describe the main features of Ants-Review.
\paragraph{Incentivisation and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[4]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[5]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.
\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews on the same manuscript can have their tokens accrue interest over time (see 3.2).

\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and editors' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[6]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').

@@

\subsection{A new community-driven standard?}
As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incetivization mechanisms. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might set a first step in this standardization. We hope that soon the value of peer review as public good will be recognized by research funders and hiring committees.

>>>>

\subsection{Related work} Some mild attempts to credit peer review have been handled without much success by journals via attribution of virtual 'badges', certificates of performance, citation in annual editorials where performance, though, is assessed only in terms of quantity of reviews but not quality.
\newline REVIEWER RECOGNITION SERVICE FOR PUBLISHERS\emph{Publons}\footnote[1]{\emph{Publons}.\textsc{URL:} https://publons.com/about/home.}, integrated with ORCID (researcher identifier), that provides a reputational system of peer-review metric based on authors' prolificacy of reviews; \emph{Peerage of Science}\footnote[2]{\emph{Peerage of Science}.\textsc{URL:} https://www.peerageofscience.org.} and \emph{ResearchSquare}\footnote[3]{\emph{ResearchSquare}.\textsc{URL:}https://www.researchsquare.com.} that provide scientific peer review and also peer-reviews of the reviews.
\newline Alternative proposals to improve the peer-review system with an incentivization mechanism on the blockchain have been made by Spearpoint \cite{ResearchCoin} who proposes \emph{r-coin} (for ‘ReviewCoin’ or ‘ResearchCoin’), a cryptocurrency that researchers earn for undertaking peer-reviews and that can used to pay for publication fees; \emph{ScienceMiles} \cite{ScienceMiles} is a cryptocurrency for incentivizing peer-reviews through a blockchain-based platform and an open peer-review process; Avital \cite{AvitalToken} suggests a token-based peer-review payment system; \emph{INFINITCODEX (I8X)} \cite{I8X}, is a platform that promotes cooperative user behaviour through dynamic research papers that undergo  continuous peer review process. The system implements cryptoeconomical incentives for building reputation in the community of users. \emph{Decentralized Science} \cite{DecentralSc2,DecentralSc1}, \emph{Pevo}\cite{Pevo}, \emph{CryptSubmit}\cite{CryptSubmit} and \emph{MarsChain}\cite{MarsChain} have instead respectively focused on features such as decentralization and security.

@@

Here we describe the main features of Ants-Review.
\paragraph{Incentivization and recognition.} A popular incentive model for open source software (OSS) is represented by Bounties. Bounties are a prize or monetary rewards given for completing a task before a deadline \cite{BountyGit}. Examples of such platforms that allow funders (bounty backers) to pay developers (bounty hunters) for open source contributions are \emph{Gitcoin}\footnote[4]{\emph{Gitcoin}.\textsc{URL:} https://gitcoin.co.} and \emph{The Bounties Network}\footnote[5]{\emph{The Bounties Network}.\textsc{URL:}https://bounties.network.}. Incentives can be represented by tokens, unit of values registered on a blockchain network, that represent the quantity and quality of a service within a network.
\newline In the network of the scientific community reviewers provide a service and those who consume it (authors, journals) should be able to contribute with tokens. The amount of tokens reflects material and symbolic recognition of the performed work that can be statistically quantified for author-level metrics measuring the productivity and impact of a researcher.
Thus, the system acts also as a reputation builder.
\newline Moreover, to encourage commitment, reviewers who contribute consistently to multiple rounds of reviews on the same manuscript can have their tokens accrue interest over time (see 3.2).

\paragraph{Transparency and re-usability of the records.} The peer-review history, including authors' replies and reviewers' recommendations, should be openly and permanently accessible to the community (in the form of 'open reports' of open peer-reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer-review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[6]{\emph{Neuroscience Peer Review Consortium}.\textsc{URL:}http://nprc.incf.org.} and independent companies like \emph{ResearchSquare}  and \emph{Peerage of Science}, peer-reviews in Ants-Review will be transferable across journals (like in 'cascading' or 'portable peer-reviews').

@@

\subsection{A new community-driven standard?}
As Tennant points out\cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). If also pre-print platforms integrate peer-review into their platforms, the dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by alternative peer-review platforms and justify their added value (\emph{ibidem}).
In our proposal we decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process might require a new standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[20]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might set a first step in this standardization. We hope that soon the value of peer review as public good will be recognized by research funders and hiring committees.
